Software

### 2025-01-22 software.qmd
add cran link

>>>>

## `veesa`
I'm a devloper of the `veesa` R package ([CRAN](https://cran.r-project.org/web/packages/veesa/index.html);[GitHub](https://github.com/sandialabs/veesa)).

A R package for VEESA Pipeline for Explainable Machine Learning with Functional Data frin oaoer K. Goode, J. D. Tucker, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Annals of Applied Statistics*, submitted, 2025.
